Toward Automatic Translation from OpenACC to OpenMP 4

### 2016-04-21 sig-alternate-sample.tex
Added grammar and translation rules

>>>>

\begin{figure}
\begin{tabular}{rcl}
\textit{acc-directive} &$\rightarrow$& \texttt{\#pragma acc data\ }\textit{data-clauses} \\
                       &     $|$     & \texttt{\#pragma acc parallel loop} \\
                       &     $|$     & \texttt{\#pragma acc parallel} \\
                       &     $|$     & \texttt{\#pragma acc loop\ }\textit{loop-clauses} \\
\textit{data-clause}   &$\rightarrow$& \texttt{copyin(}\textit{vars}\texttt{)} \\
                       &     $|$     & \texttt{copyout(}\textit{vars}\texttt{)} \\
                       &     $|$     & \texttt{create(}\textit{vars}\texttt{)} \\
\textit{loop-clause}   &$\rightarrow$& \texttt{independent} \\
                       &     $|$     & \texttt{private(}\textit{vars}\texttt{)} \\
                       &     $|$     & \texttt{reduction(}\textit{reductions}\texttt{)} \\
\end{tabular}
\caption{OpenACC subset grammar accepted by the translation tool.  The syntax
of \textit{vars} and \textit{reductions} is omitted.  The nonterminals
\textit{data-clauses} and \textit{loop-clauses} correspond to sequences of zero
or more phrases derived from \textit{data-clause} and \textit{loop-clause},
respectively.}
\label{fig:grammar}
\end{figure}

\newcommand{\translate}[1]{\ensuremath{\mathcal{T}[\![ #1 ]\!]}}
\begin{figure*}
\begin{align*}
%
\translate{\texttt{\#pragma acc data\ }\textit{data-clauses}} &=
   \texttt{\#pragma omp target data } \translate{\textit{data-clauses}} \\
%
\translate{\texttt{copyin(}\textit{vars}\texttt{)}} &=
   \texttt{map(to:}\textit{vars}\texttt{)} \\
%
\translate{\texttt{copyout(}\textit{vars}\texttt{)}} &=
   \texttt{map(from:}\textit{vars}\texttt{)} \\
%
\translate{\texttt{create(}\textit{vars}\texttt{)}} &=
   \texttt{map(alloc:}\textit{vars}\texttt{)} \\
%
\translate{\texttt{\#pragma acc parallel loop}} &=
   \left\{\parbox{2in}{%
   \texttt{\#pragma omp target} \\
   \texttt{\#pragma omp teams} \\
   \texttt{\#pragma omp distribute}}\right. \\
%
\translate{\texttt{\#pragma acc parallel}} &= %\textit{parallel-clauses}} &=
   \left\{\parbox{2in}{%
   \texttt{\#pragma omp target} \\
   \texttt{\#pragma omp teams}}\right. \\
%
\translate{\texttt{\#pragma acc loop\ }\textit{loop-clauses}} &=
   \texttt{\#pragma omp parallel for\ }\textit{loop-clauses} \\
%
\end{align*}
\caption{Translation rules from OpenACC to OpenMP~4.  The function
$\mathcal{T}$ maps an OpenACC directive to a sequence of one or more OpenMP
directives.}
\label{fig:rules}
\end{figure*}
